Glyph-maps for visualizing climate data and models

### 2011-08-26 paper.tex
math for polar coordinates adjusted to code

\documentclass[oneside]{article}
\usepackage{fullpage}
\usepackage[pdftex]{graphicx}
\DeclareGraphicsExtensions{.png,.pdf}
\graphicspath{{images/}}
\usepackage{hyperref}
\usepackage{verbatim}
\usepackage[format=plain,font=small]{caption}
\usepackage[small]{titlesec}
\usepackage[round,sectionbib]{natbib}
\bibliographystyle{plainnat}
\renewcommand\rmdefault{bch}
\linespread{1.07}

@@

The pre-processing step is simple, once you notice that the position of graphical elements is determined by a major and minor axis in each direction (x and y). For maps, the major axes are latitude and longitude, and the minor axes are typically time on the x-axis and some measurement or model prediction on the y-axis. The final locations are a simple linear combination.  After rescaling the minor axis to have range $[0, 1]$, the $x$ coordinate is given by $x_{major} + w \cdot x_{minor}$ and $y$ by $y_{major} + h \cdot y_{minor}$, where $w$ and $h$ are width and height respectively

Because the x and y locations are linear combinations of two variables, these types of displays can also be built interactively by software that supports tours \citep{cook:2006}, such as DataViewer \citep{buja:1986}, XGobi \citep{swayne:1991} or GGobi \citep{swayne:2003}.  This technique is used to good effect in \citet{buja:1996a}.

Computing the coordinates for star glyphs is equally easy. Without loss of generality, we assume that $y_{minor}$ becomes $r$, the radius, and $x_{minor}$ becomes $\theta$, the angle, both rescaled to lie between 0 and 1. Then the glyph $x$ coordinate is given by $x_{major} + \frac{w \cdot r}{2} \cos(2 \pi \theta)$, and the $y$ coordinate by $y_{major} + \frac{h \cdot r}{2} \sin(2 \pi \theta)$.

>>>>

\documentclass[oneside]{article}
\usepackage{fullpage}
\usepackage[pdftex]{graphicx}
\DeclareGraphicsExtensions{.png,.pdf}
\graphicspath{{images/}}
\usepackage{hyperref}
\usepackage{verbatim}
\usepackage[format=plain,font=small]{caption}
\usepackage[small]{titlesec}
\usepackage[round,sectionbib]{natbib}
\usepackage{amstext}
\bibliographystyle{plainnat}
\renewcommand\rmdefault{bch}
\linespread{1.07}

\newcommand\amin{\text{minor}}
\newcommand\amaj{\text{major}}

@@

The pre-processing step is simple, once you notice that the position of graphical elements is determined by a major and minor axis in each direction ($x$ and $y$). For maps, the major axes are latitude and longitude, and the minor axes are typically time on the $x$-axis and some measurement or model prediction on the $y$-axis. The final locations are a simple linear combination.  After rescaling the minor axis to have range $[0, 1]$, the $x$ coordinate is given by $x_{\amaj} + w \cdot x_{\amin}$ and $y$ by $y_{\amaj} + h \cdot y_{\amin}$, where $w$ and $h$ are width and height respectively

Because the $x$ and $y$ locations are linear combinations of two variables, these types of displays can also be built interactively by software that supports tours \citep{cook:2006}, such as DataViewer \citep{buja:1986}, XGobi \citep{swayne:1991} or GGobi \citep{swayne:2003}.  This technique is used to good effect in \citet{buja:1996a}.

Computing the coordinates for star glyphs is equally easy. Without loss of generality, we assume that $y_{\amin}$ becomes $r$, the radius, and $x_{\amin}$ becomes $\theta$, the angle, both rescaled to lie between 0 and 1. Then the glyph $x$ coordinate is given by $x_{\amaj} + \frac{w \cdot r}{2} \sin(2 \pi \theta)$, and the $y$ coordinate by $y_{\amaj} + \frac{h \cdot r}{2} \cos(2 \pi \theta)$.
